\begin{rubric}{Professional Experience}

\entry*[2024--2025]
    \textbf{Yoh, A Day \& Zimmerman Company --- Remote, SC} \emph{ADF Solution Architect – Core Specialty Insurance} \begin{itemize}
        \item Built a small SDE team and delivered an MVP Insurance Data Ingestion Platform using Microsoft's Common Data Model, reducing time-to-ingest by \textbf{50\%}.
        
        \item Architected and implemented an API to orchestrate Azure Data Factory pipelines and data flows.
        
        \item Prototyped LLM-assisted source-to-target mapping generating ADF transformations and derived columns.
        
        \item Built a Streamlit UI integrated with the Data Ingestion API for faster analyst feedback loops.
    \end{itemize}

\entry*[2021--2023]
    \textbf{Duck Creek Technologies --- Columbia, SC} \emph{Senior Technical Architect – OnDemand SaaS Operations} \begin{itemize}
        \item Led first client launch on accelerated 3-month timeline with automated deployments to Azure Storage, Key Vault, Redis, and Docker.
        \item Designed end-to-end data integration/transformation across hybrid SaaS systems.
        \item Drove ADF implementation connecting Duck Creek data with customer Data Lakes.
        \item Built deployment analysis framework (C\#, PowerShell, Octopus, ADO) eliminating \textbf{75\%} of deployment issues.
        \item Developed Python algorithm to predict Sev~1 incidents from logs.
    \end{itemize}

    \entry*[2016--2020]
        \textbf{Blackbaud --- Charleston, SC} \emph{Principal Engineer – Sustained Engineering} \begin{itemize}
            \item Delivered root-cause production fixes across enterprise products using C\#, SQL, and performance tooling; achieved \textbf{100\%} resolution on critical cases.
            \item Cut deployment time and customer involvement by \textbf{50\%} via DevOps scripting and YAML pipelines.
            \item Met \textbf{100\% SLA} for Tier 3 support, improving VB.NET, C\#, and Java systems.
            \item Designed SAML 2.0 SSO component; published REST APIs to Azure using Swagger-based codegen.
        \end{itemize}
    
    \entry*[2011--2016]
        \textbf{Blackbaud --- Charleston, SC} \emph{Solution Architect – Enterprise Professional Services} \begin{itemize}
            \item Led multiple enterprise implementations from architecture to go-live; coordinated global teams.
            \item Designed full CRM integrations and migration strategies, reducing timelines by \textbf{50\%}.
            \item Built Azure environments for development and CI/CD.
        \end{itemize}
    
    \entry*[2005--2011]
        \textbf{DJJayNet Consulting --- Arlington, VA}
        \emph{Software Engineering Consultant}
        \begin{itemize}
            \item Integrated user interfaces with Crestron touch hardware using custom .NET controls.
            \item Implemented REST APIs with Entity Framework and C\#.
        \end{itemize}
    
\end{rubric}